How predictable is extinction?

### 2019-06-20 doc/napc2019_talk.tex
working on napc talk
talk ready for napc?

\documentclass{beamer} 
\usepackage{amsmath,amsthm}
\usepackage{graphicx,microtype,parskip}
\usepackage{caption,subcaption,multirow}
\usepackage{attrib}
\usepackage{array}

@@

        \includegraphics[width=\textwidth,height=0.15\textheight,keepaspectratio=true]{figure/dino}

@@

        \attrib{\footnotesize{UCL}}
      \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/occ_time_label_full}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/age_label_full}
    \end{column}
  \end{columns}

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes our historical covariates and allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item Models only average/fair expected out-of-sample performance.
      \end{itemize}
    \item Mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}

>>>>

\documentclass[aspectratio=169]{beamer} 
\usepackage{amsmath,amsthm}
\usepackage{graphicx,microtype,parskip}
\usepackage{caption,subcaption,multirow}
\usepackage{attrib}
\usepackage{array}

@@

        \includegraphics[width=\textwidth,height=0.15\textheight,keepaspectratio=true]{figure/diatom}

@@

        \attrib{\footnotesize{UCL}}
      \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.7\textheight,keepaspectratio=true]{../results/figure/occ_time_label_full}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.7\textheight,keepaspectratio=true]{../results/figure/age_label_full}
    \end{column}
  \end{columns}

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes either our historical covariates or allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item Models only average/fair expected out-of-sample performance.
      \end{itemize}
    \item Allowing effects to vary over time is probably preferable to historical covariates -- measures and accounts for variation which is important when predicting extinction in novel environments.
    \item Mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}

\begin{frame}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{figure/book}

    \Large{https://psmits.github.io/paleo\_book/index.html}
  \end{center}
